Natural language processing is a difficult problem,
but as a state-of-the-art fictional robot,
geometric idioms with non-geometric meanings,
such as ``take it back''
meaning ``apply the inverse of the most recently applied operator'',
are robot-with-factory-settings's play.
You therefore roll your robot wheels rightwards
in perfect execution of the expected dance mo---

\emph{Crash!}

You bump into a backwards-moving human,
who yells in surprise and spills her drink on you.
It appears you did not perform the expected dance move.
Worse still, the drink is dangerously conductive!
You must locate a cleaning station and remove the spill
before you short-circuit.
Fortunately, the human is willing to help:
she spontaneously apologizes for not seeing you there
and offers to show you to a ``bathroom'' to clean up.
Hoping that a bathroom contains suitable cleaning supplies,
you follow her.

Upon entering the human bathroom,
you discover it to be a curious colocation of cleaning stations
and waste disposal stalls.
You wipe off the dangerously conductive beverage
and decide that, while you are here,
you may as well empty Waste Disposal Bays~\#1 and~\#2.
After reviewing a recent paper on human waste-disposal protocol
\citep{sarah_ziv},
you enter a stall.
As you position your Waste Disposal Bays, you hear the door open:
another human is here for waste disposal.

\begin{switch}
\item{WAIT\_FOR\_IT}
  Empty Waste Disposal Bay~\#1.
  \goto{bathroom-stealth}
\item{GO\_FOR\_IT}
  Empty Waste Disposal Bays~\#1 and~\#2.
  \goto{end-bathroom}
\end{switch}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "message-from-pc"
%%% End:
