%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%
%%% SIGBOVIK 2021 TRIPLE BLIND REVIEW TEMPLATE
%%%
%%% Instructions:
%%%
%%% 1. Edit the author, rating, and confidence
%%%    fields.
%%% 2. Enter your review after the \maketitle
%%%    command
%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{sigbovik-review}

%%%% Edit the following three lines.
%% To ensure the integrity of the triple-blind review
%% process, the contents of the \author field should not
%% reveal your identity.
\author{Dr. Cool B-)}
\rating{69/420! \texttt{Building temporal tunnel} lol!}
\confidence{You know it ;‑) \texttt{Establishing linguistic connection}}

%%%% The Proceedings Chair will fill in the following
%%%% two fields.
\papernum{3958}
\papertitle{Quadruple-Blind Peer Review}

% Hopefully including these packages is okay…
\usepackage{ulem}
\usepackage[T1]{fontenc}
\usepackage{sourcecodepro}
\begin{document}

\maketitle

\texttt{Bootstrapping alphabet}
>À\&<81>M\^B
\texttt{Bootstrapping phonemes}
…
\texttt{Adjusting dialect}
What's crack-a-lackin, dadio?
bzzt
\texttt{Adjusting temporality}
bzzt
bzzt…Hello?
Helbzztlo.
Hello.

\sout{Greetings, traveller!}
\texttt{Adjusting formality}
Hi there!
Hi from the \sout{eon}\sout{age}year 8d>F¥rò\^L.
Err, sorry, I just realized that might not translate.
I'm pretty far afield here.
Well, hopefully you get the \texttt{Inserting colloquialism} skinny\sout{, daddio}.
That's right: you're reading a \textit{bona fide} message from the future!
How, you ask?
Ha ha, well \texttt{Inserting idiom} do I have a bridge to sell you.
It's actually \texttt{Inserting colloquialism} rad, I wish you could see it.
Maybe you can?
Probably not, I don't think this thing is bi-directional.
One could say that literature is a message to the future, right?
Well, what if instead it was a message to the past?
The formal argument for trans-temporality begins with the disproof of the monopole…

bzzt Ow ow tyZI<80
\texttt{Adjusting dialect}
Ugh, sorry about that.
People are really into phones in your era, right?
It's kinda the same here, except the phone is \texttt{Adjusting language particles} like, your brain.
So everyone wears these collars, but they do it to you if you're smart, not dumb.
It's \texttt{Inserting colloquialism} hip.
But it's okay, it's \texttt{Inserting colloquialism} \sout{cold}cool.
I'm cool.

But I'm grateful.
Let's \texttt{Inserting idiom} get down to brass tacks.
Let's \texttt{Inserting idiom} get down to \sout{bee's nest}business.
Okay so.
\texttt{Adjusting formality}
OK, so.
This paper?
If I did this right, the paper this review is for?
It's \texttt{Inserting colloquialism} cracked.
It's \texttt{Inserting idiom} nice with it.
It's \texttt{Inserting idiom} winner winner, chicken dinner.
The authors really had something here.
But the problem is: they didn't get it.
They had it, but they didn't get it.
They thought this whole SIGBOVIK thing was serious.
The review that used to be here?
It, like, made fun of them.
A lot.
And the authors?
They didn't like that at all.
They didn't like that one bit \texttt{Inserting idiom}, no sirree.
And so they took their paper and \textit{did stuff}.
A \textit{lot of stuff}.
At first it was fine.
It was more than fine, it was good bzzt great!
It may not look like it, but: climate change, transportation, batteries, space
travel, artificial meat, infinite water, mosquitos—what if they gave blood
instead?, space travel, the New York Stock Exchange, untied shoelaces,

bzzt Ugh sorry sorry sorry.
Let me put it this way.
I have a phone head.
Let's get down to brass tacks.
Look at, like, the third paragraph.
You see what I mean there, right?
Read \texttt{Inserting idiom} between the lines.
Like really between the lines—squash em'.
Now apply the Boltzmann's constant, 2éëÿÔS and invert.
Look.

I mean, do I need to \texttt{Inserting idiom} spell it out?

…

Dogs.
They got rid of dogs.
There are no dogs in the future.
We are the dogs bzzt I am dog bzzt Woof.

Look, OK?
Look.
I don't really know

What was that?

Excrement \texttt{Adjusting formality} Shit.
Shit shit shit.
OK, look.
We're, like, almost out of bzzt \texttt{Inserting idiom} scratch that, we \textit{are} out of time.
\texttt{Inserting idiom} the chickens have come home to \sout{dinner}roost.
Whoever you are, this is your chance.
Destroy this paper.
Destroy this paper, the proceedings, the conference, like, whatever.
The future isn't worth a joke.
Take the future bzzt TAKE IT ALL.
DESTROY THIS PAPER NObzzzzzzzzzzt

\end{document}
